% !TEX root = ../main.tex
\subsubsection{Formation Time}
\label{sssec::formation_time}
    In the final stage of the hadronisation process, the struck quark finds partner quarks to neutralise its colour, thus ending the gluon radiation.
    This stage is characterised by the evolution of the pre-hadron to an ordinary hadron, and is commonly name
    The formation time is the time required to form the colour field of a hadron.
    This time should depend on the hadron being formed.

    Formation time is not directly related to confinement, but rather is a measure of the time required to form the non-perturbative colour field of the hadron, starting from a small colour-singlet object.
    This field generation time has a well known analogue in Quantum Electrodynamics (QED).

    We can build a simple estimate for the formation time.
    To form an hadron of radius $R$ from a point-like, single-colour singlet, the speed at which the field can arise (in its rest frame) is bound by the speed of light
    \begin{equation*}
        \tau^\text{rest}_\text{formation} > \frac{R}{c},
    \end{equation*}
    which, Lorentz-boosted into the lab frame, is
    \begin{equation*}
        \tau^\text{lab}_\text{formation} > \frac{E}{m^*} \frac{R}{c},
    \end{equation*}
    where $m^*$ is the mass of the propagating colour-singlet object.
    In principle, $m^*$ ranges from the mass of two bare quarks to the fully formed hadron mass $m_h$.
    Then, a lower limit for the formation time is given by setting $m^* = m_h$.

    While this estimate is a classical calculation, a quantum mechanical analysis taking into account gluon wavelength arrives at the same result \cite{dokshitzer1991}.

    For a concrete example, for a $10$ GeV pion -- mass of $0.139$ GeV and radius of $0.7$ fm --, the formation time should be at least $50.4$ fm.
    Thus, in total, one can expect a pion production time of $3.3$ fm and formation time of at least $50.4$ fm in the lab frame at JLab energies.
