% !TEX root = ../main.tex
\subsubsection{Slow Control System}
\label{sssec::slowcontrolsystem}
% --+ What is slow control +----------------------------------------------------
    A modern experimental physics experiment usually involves many moving parts and complex components that require constant monitoring and calibration.
    Additionally, continuous data collection is necessary.
    This task is accomplished through the use of slow control systems.
    These systems typically integrate the entire detector and experiment into one complex interface, facilitating easy access and maintenance.

% --+ What is EPICS +-----------------------------------------------------------
    The standard framework used in the context of HEP for achieving this is the Experimental Physics and Industrial Control System (EPICS).
    EPICS was developed at the Los Alamos National Laboratory (ANL) to facilitate data acquisition and control for such experiments.
    This framework offers a distributed process control system that includes software communication, functional subsystems for data acquisition, supervisory control, closed-loop control, channel archiving, and alarm management \cite{dalesio1991}.

    Similar to many HEP experiments, the slow control system of CLAS12 is based on EPICS \cite{boyarinov2020}.

% --+ EPICS installation on raspi +---------------------------------------------
    To enable the integration of the RG-E target into the CLAS12 slow control system, the author developed an EPICS support module and Input/Output Controller (IOC).
    This module was not created from scratch since the motor developers had already developed a generic support module for Galil motors \cite{farnswort2009}.
    The existing system proved to be capable of supporting the movement of the RG-E target system, requiring only the removal of unnecessary features and the addition of experiment-specific database variables.

    The RG-E IOC, along with the complete set of EPICS support modules necessary to run it, can be found at

    \begin{center}
        \hyperlink{https://github.com/bleaktwig/rge-epics-support}{\texttt{https://github.com/bleaktwig/rge-epics-support}}.
    \end{center}

    The EPICS module includes Process Variables (PVs) that have been added to facilitate the control of the RG-E target system.
    Below is a list of these PVs along with a brief description of each.
    The user-defined records database, where these PVs can be viewed and edited, is located at

    \begin{center}
        \texttt{\$EPICS\_BASE/support/galil/3-6/db/galil\_userdef\_records.template}.
    \end{center}

    \input{11experiment/311process_variables}
    \input{11experiment/312cs_studio}
    \input{11experiment/313alarm_system}
