% !TEX root = ../main.tex
\section*{Acknowledgements}
    % Family.
    % -- Eli.
    First, I want to thank my fiancé Eli for being the best.
    Without your support I would have surely collapse long before finishing this thesis.
    % -- Paula.
    Continuing on family, I give a big thank you to my sister Paula.
    Your company (and patience towards my lack of housework) allowed for a great way to vent work-related stress.
    % -- Oma, Isabel, and Walter.
    Finally, I also want to thank my Oma Hedi, my mother Isabel, and my father Walter for their counsel and love.

    % JLab staff.
    % -- Raffaella.
    Moving towards JLab, I want to express my deepest gratitude towards Raffaella De Vita.
    Working with you has truly been the greatest part of my physics career so far, and I hope to continue aiding you and the lab in whatever way I can.
    % -- FMT Alignment peoples.
    On the same line, I want to thank Veronique Ziegler and Maxime Defurne, for their counsel and aid during the FMT alignment work.
    % -- RG-F peoples.
    I also want to thank Sebastian Kuhn, Mohammad Hattawy, and Yu-Chun Hung from RG-F, who helped me get started working with their data.
    % -- Nathan.
    Then, a thank you to Nathan Baltzell for his very abundant help with reconstruction and slow controls system.
    % -- Stepan, Maurizio, and Gagik.
    I also want to thank Stepan Stepanyan, Maurizio Ungaro, and Gagik Gavalian for showing me around the lab and making my stay there all-around better.

    % RG-E.
    % -- Higher-ups.
    Regarding RG-E, I want to thank Hayk Hakobyan for assisting and pushing me to finish this thesis.
    I want to thank Will Brooks as well, for his pinpoint questions and wise answers.
    Then my concert companion Taisiya Mineeva as well, for her dilligence in organizing the group and always providing interesting conversation subjects.
    % -- Folks.
    From the group, I also want to thank my fellow students Esteban Molina, Antonio Radic, Claudio San Martín, and Matías Barria.
    While very distracting, sitting alongside you makes work so much more entertaining, and your help with ROOT is almost as invaluable as ChatGPT's.
    % -- Target group.
    Then, I want to thank the target group, whose composition during my tenure was Sebastián Gálvez, Eduardo Valdivia, Jairo Gonzales, and Alonso Lepe.

    % Misc.
    Some final thank yous I couldn't fit anywhere else:
    To Nicole Benz and Loreto Romero, for their friendship and emotional support during (and outside) work hours.
    To Oscar Castillo, for the long and fun conversations about both jazz and physics.
    And finally to Mark Clift from Galil, for providing so much help in the use of EPICS for the Galil motor.
